Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-01 sports_analytics.Rmd
added Albert reference
added Marchi reference
added sections

See [blah] for examples of analytical findings that are based on the expected run matrix.

## In other sports

@@

>>>>

See @Albert2001curve for a fuller discussion of the use of the expected run matrix in baseball and @marchi2018analyzing for examples of how to estimate the expected run matrix using Retrosheet data.

## In other sports with discrete states

@@

## Sports with continuous states
